A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Electron Beam Dynamics

### 2019-02-01 paper/submission/prab.tex
fixing bib for resubmission
adding bib to tex file and moving figures

\begin{figure}%[h!]
	\center
\includegraphics[width=0.5\textwidth]{figures/opt-framework_code}
\caption{Multi-objective framework: the pilot (master) solves the
	optimization problem specified in the input file by coordinating optimizer
	algorithms and workers running forward solves.}
\label{fig:framenetwork}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{figures/ga_explained_big}
  \caption{Schematic view of interplay between selector and variator. The
  selector ranks all individuals in the population according to fitness and
  subsequently the variator uses the fittest individuals to produces new
  offspring. Finally, the new children are reintroduced in the population.}
  \label{fig:varsel}
\end{figure}

@@

The basic assumption in simulation-based optimization is that a
  call to an expensive simulation software component present in the
  constraints or objectives is needed.
The framework is divided in three exchangeable components, as shown in
  Fig.~\ref{fig:opt-framework-layout}, to encapsulate the major behavioral
  patterns of the framework.
%
\begin{figure}
  \centering
  \includegraphics[width=0.7\linewidth]{figures/opt-framework-layout}
  \caption{Schematic view of messages passed within the network between the
    three roles.
  The dashed cyan path describes a request (job $j_1$) sent from $O_i$ to the
  \textsc{Pilot} being handled by $W_j$. Subsequently the result $r_k$ is
  returned to the requesting \textsc{Optimizer} ($O_i$). The work $W_j$ are beam dynamics 
  simulation within OPAL.}
  \label{fig:opt-framework-layout}
\end{figure}

@@

	\begin{widetext}
		\begin{align} \label{eqn:bench}
		\text{min} & \left[ 1 - \exp \left( -1 \left(
		\left(x_1 - \frac{1}{\sqrt{3}} \right)^2 +
		\left(x_2 - \frac{1}{\sqrt{3}} \right)^2 +
		\left(x_3 - \frac{1}{\sqrt{3}} \right)^2 \right)\right), \right. \\
		\vspace{3em} 
		& \left. 1 - \exp \left( -1 \left(
		\left(x_1 + \frac{1}{\sqrt{3}} \right)^2 +
		\left(x_2 + \frac{1}{\sqrt{3}} \right)^2 +
		\left(x_3 + \frac{1}{\sqrt{3}} \right)^2 \right)\right) \right]^T \nonumber \\
		\vspace{3em} \nonumber \\
		\text{s.t.} \quad & \quad -1 \le x_i \le 1, \quad i=1,2,3 \nonumber
		\text{.} \nonumber
		\end{align}
	\end{widetext}
%\end{strip}

@@

% AA: this is too much for Phys Rev. AB

% \appendix

%\section{Forward Solver Implementation}
%
%A simple implementation, e.g.\ using a Python forward solver, is given below
%  in Listing 6.
%We assume the Python script executes a simulation and dumps results in the
%  \textsc{SDDS} file format~\cite{borl:00}.
%Utility classed are used to parse the result data and fill the appropriate
%  structures returned to the optimizer algorithm.
%
%\begin{code}[Simple Simulation Wrapper]
%#include <map>
%#include <string>
%#include <vector>
%
%#include "Util/Types.h"
%#include "Util/CmdArguments.h"
%#include "Simulation/Simulation.h"
%
%#include "boost/smart_ptr.hpp"
%
%class SimpleSimulation : public Simulation {
%
%public:
%
%    SimpleSimulation(Expressions::Named_t objectives,
%                     Expressions::Named_t constraints,
%                     Param_t params, std::string name, MPI_Comm comm,
%                     CmdArguments_t args);
%
%    ~SimpleSimulation();
%
%    /// Calls simulation through Python wrapper and returns when simulation
%    /// has either failed or finished.
%    void run() {
%        // user implements wrappers
%        prepare_input_file();
%        run_python_simulation();
%    }
%
%    /// Parse SDDS stat file and build up requested variable dictionary.
%    void collectResults(){
%
%        Expressions::Named_t::iterator it;
%        for(it = objectives_.begin(); it != objectives_.end(); it++) {
%
%            Expressions::Expr_t *objective = it->second;
%
%            // find out which variables we need in order to evaluate the
%            // objective
%            variableDictionary_t variable_dictionary;
%            std::set<std::string> req_vars = objective->getReqVars();
%
%            if(req_vars.size() != 0) {
%
%                boost::scoped_ptr<SDDSReader> sddsr(new SDDSReader(fn));
%
%                try {
%                    sddsr->parseFile();
%                } catch(OptPilotException &e) {
%                    std::cout << "Exception while parsing SDDS file: "
%                        << e.what() << std::endl;
%                    break;
%                }
%
%                // get all the required variable values from the stat file
%                foreach(std::string req_var, req_vars) {
%                    if(variable_dictionary.count(req_var) == 0) {
%
%                        try {
%                            double value = 0.0;
%                            sddsr->getValue(1 /*atTime*/, req_var, value);
%                            variable_dictionary.insert(
%                                std::pair<std::string, double>(req_var, value));
%                        } catch(OptPilotException &e) {
%                            std::cout << "Exception while getting value "
%                                      << "from SDDS file: " << e.what()
%                                      << std::endl;
%                        }
%                    }
%                }
%            }
%
%            // and evaluate the expression using the built dictionary of
%            // variable values
%            Expressions::Result_t result =
%                objective->evaluate(variable_dictionary);
%
%            std::vector<double> values;
%            values.push_back(boost::get<0>(result));
%            bool is_valid = boost::get<1>(result);
%
%            reqVarInfo_t tmps = {EVALUATE, values, is_valid};
%            requestedVars_.insert(
%                std::pair<std::string, reqVarInfo_t>(it->first, tmps));
%
%        }
%    }
%
%    /// returns container containing all requested variables with results
%    reqVarContainer_t getResults() { return requestedVars_; }
%
%private:
%
%    /// holds solutions returned to the optimizer
%    reqVarContainer_t requestedVars_;
%
%    Expressions::Named_t objectives_;
%    Expressions::Named_t constraints_;
%
%    MPI_Comm comm_;
%};
%
%#endif
%\end{code}

\bibliography{paper}

>>>>

\begin{figure}%[h!]
	\center
\includegraphics[width=0.5\textwidth]{opt-framework_code}
\caption{Multi-objective framework: the pilot (master) solves the
	optimization problem specified in the input file by coordinating optimizer
	algorithms and workers running forward solves.}
\label{fig:framenetwork}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{ga_explained_big}
  \caption{Schematic view of interplay between selector and variator. The
  selector ranks all individuals in the population according to fitness and
  subsequently the variator uses the fittest individuals to produces new
  offspring. Finally, the new children are reintroduced in the population.}
  \label{fig:varsel}
\end{figure}

@@

The basic assumption in simulation-based optimization is that a
  call to an expensive simulation software component present in the
  constraints or objectives is needed.
The framework is divided in three exchangeable components, as shown in
  Fig.~\ref{fig:opt-framework-layout}, to encapsulate the major behavioral
  patterns of the framework.
%
\begin{figure}
  \centering
  \includegraphics[width=0.7\linewidth]{opt-framework-layout}
  \caption{Schematic view of messages passed within the network between the
    three roles.
  The dashed cyan path describes a request (job $j_1$) sent from $O_i$ to the
  \textsc{Pilot} being handled by $W_j$. Subsequently the result $r_k$ is
  returned to the requesting \textsc{Optimizer} ($O_i$). The work $W_j$ are beam dynamics 
  simulation within OPAL.}
  \label{fig:opt-framework-layout}
\end{figure}

@@

	\begin{widetext}
		\begin{align} \label{eqn:bench}
		\text{min} & \left[ 1 - \exp \left( -1 \left(
		\left(x_1 - \frac{1}{\sqrt{3}} \right)^2 +
		\left(x_2 - \frac{1}{\sqrt{3}} \right)^2 +
		\left(x_3 - \frac{1}{\sqrt{3}} \right)^2 \right)\right), \right. \\
		\vspace{3em} 
		& \left. 1 - \exp \left( -1 \left(
		\left(x_1 + \frac{1}{\sqrt{3}} \right)^2 +
		\left(x_2 + \frac{1}{\sqrt{3}} \right)^2 +
		\left(x_3 + \frac{1}{\sqrt{3}} \right)^2 \right)\right) \right]^T \nonumber \\
		\vspace{3em} \nonumber \\
		\text{s.t.} \quad & \quad -1 \le x_i \le 1, \quad i=1,2,3 \nonumber
		\text{.} \nonumber
		\end{align}
	\end{widetext}

@@

%\bibliography{paper}
\providecommand{\SortNoop}[1]{}
\begin{thebibliography}{37}%
	\makeatletter
	\providecommand \@ifxundefined [1]{%
		\@ifx{#1\undefined}
	}%
	\providecommand \@ifnum [1]{%
		\ifnum #1\expandafter \@firstoftwo
		\else \expandafter \@secondoftwo
		\fi
	}%
	\providecommand \@ifx [1]{%
		\ifx #1\expandafter \@firstoftwo
		\else \expandafter \@secondoftwo
		\fi
	}%
	\providecommand \natexlab [1]{#1}%
	\providecommand \enquote  [1]{``#1''}%
	\providecommand \bibnamefont  [1]{#1}%
	\providecommand \bibfnamefont [1]{#1}%
	\providecommand \citenamefont [1]{#1}%
	\providecommand \href@noop [0]{\@secondoftwo}%
	\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
	\providecommand \@href[1]{\@@startlink{#1}\@@href}%
	\providecommand \@@href[1]{\endgroup#1\@@endlink}%
	\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
		`\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
	\providecommand \@@startlink[1]{}%
	\providecommand \@@endlink[0]{}%
	\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
	\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
	\providecommand \urlprefix  [0]{URL }%
	\providecommand \Eprint [0]{\href }%
	\providecommand \doibase [0]{http://dx.doi.org/}%
	\providecommand \selectlanguage [0]{\@gobble}%
	\providecommand \bibinfo  [0]{\@secondoftwo}%
	\providecommand \bibfield  [0]{\@secondoftwo}%
	\providecommand \translation [1]{[#1]}%
	\providecommand \BibitemOpen [0]{}%
	\providecommand \bibitemStop [0]{}%
	\providecommand \bibitemNoStop [0]{.\EOS\space}%
	\providecommand \EOS [0]{\spacefactor3000\relax}%
	\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
	\let\auto@bib@innerbib\@empty
	%</preamble>
\bibitem [{\citenamefont {Huang}(2018)}]{xiaobiao}%
\BibitemOpen
\bibfield  {author} {\bibinfo {author} {\bibfnamefont {X.}~\bibnamefont
		{Huang}},\ }\href {\doibase 10.1103/PhysRevAccelBeams.21.104601} {\bibfield
	{journal} {\bibinfo  {journal} {Phys. Rev. Accel. Beams}\ }\textbf {\bibinfo
		{volume} {21}},\ \bibinfo {pages} {104601} (\bibinfo {year}
	{2018})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Hofler}\ \emph {et~al.}(2013)\citenamefont {Hofler},
	\citenamefont {Terzic}, \citenamefont {Kramer}, \citenamefont {Zvezdin},
	\citenamefont {Morozov}, \citenamefont {Roblin}, \citenamefont {Lin},\ and\
	\citenamefont {Jarvis}}]{hofler13}%
\BibitemOpen
\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
		{Hofler}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Terzic}},
	\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Kramer}}, \bibinfo
	{author} {\bibfnamefont {A.}~\bibnamefont {Zvezdin}}, \bibinfo {author}
	{\bibfnamefont {V.}~\bibnamefont {Morozov}}, \bibinfo {author} {\bibfnamefont
		{Y.}~\bibnamefont {Roblin}}, \bibinfo {author} {\bibfnamefont
		{F.}~\bibnamefont {Lin}}, \ and\ \bibinfo {author} {\bibfnamefont
		{C.}~\bibnamefont {Jarvis}},\ }\href {\doibase 10.1103/PhysRevSTAB.16.010101}
{\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. ST Accel. Beams}\
	}\textbf {\bibinfo {volume} {16}},\ \bibinfo {pages} {010101} (\bibinfo
	{year} {2013})}\BibitemShut {NoStop}%
%%CITATION = PRSTA,16,010101;%%
\bibitem [{\citenamefont {Bazarov}\ and\ \citenamefont
	{Sinclair}(2005)}]{bazarov05}%
\BibitemOpen
\bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.~V.}\ \bibnamefont
		{Bazarov}}\ and\ \bibinfo {author} {\bibfnamefont {C.~K.}\ \bibnamefont
		{Sinclair}},\ }\href {\doibase 10.1103/PhysRevSTAB.8.034202} {\bibfield
	{journal} {\bibinfo  {journal} {Phys. Rev. ST Accel. Beams}\ }\textbf
	{\bibinfo {volume} {8}},\ \bibinfo {pages} {034202} (\bibinfo {year}
	{2005})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Yang}\ \emph {et~al.}(2009)\citenamefont {Yang},
	\citenamefont {Robin}, \citenamefont {Sannibale}, \citenamefont {Steier},\
	and\ \citenamefont {Wan}}]{yrss:09}%
\BibitemOpen
\bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
		{Yang}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Robin}},
	\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Sannibale}}, \bibinfo
	{author} {\bibfnamefont {C.}~\bibnamefont {Steier}}, \ and\ \bibinfo {author}
	{\bibfnamefont {W.}~\bibnamefont {Wan}},\ }\href {\doibase
	10.1016/j.nima.2009.08.027} {\bibfield  {journal} {\bibinfo  {journal} {Nucl.
			Instrum. Methods Phys. Res. A}\ }\textbf {\bibinfo {volume} {609}},\ \bibinfo
	{pages} {50} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Terzi\ifmmode~\acute{c}\else \'{c}\fi{}}\ \emph
	{et~al.}(2014)\citenamefont {Terzi\ifmmode~\acute{c}\else \'{c}\fi{}},
	\citenamefont {Hofler}, \citenamefont {Reeves}, \citenamefont {Khan},
	\citenamefont {Krafft}, \citenamefont {Benesch}, \citenamefont {Freyberger},\
	and\ \citenamefont {Ranjan}}]{jefferson}%
\BibitemOpen
\bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~c.~v.}\
		\bibnamefont {Terzi\ifmmode~\acute{c}\else \'{c}\fi{}}}, \bibinfo {author}
	{\bibfnamefont {A.~S.}\ \bibnamefont {Hofler}}, \bibinfo {author}
	{\bibfnamefont {C.~J.}\ \bibnamefont {Reeves}}, \bibinfo {author}
	{\bibfnamefont {S.~A.}\ \bibnamefont {Khan}}, \bibinfo {author}
	{\bibfnamefont {G.~A.}\ \bibnamefont {Krafft}}, \bibinfo {author}
	{\bibfnamefont {J.}~\bibnamefont {Benesch}}, \bibinfo {author} {\bibfnamefont
		{A.}~\bibnamefont {Freyberger}}, \ and\ \bibinfo {author} {\bibfnamefont
		{D.}~\bibnamefont {Ranjan}},\ }\href {\doibase 10.1103/PhysRevSTAB.17.101003}
{\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. ST Accel. Beams}\
	}\textbf {\bibinfo {volume} {17}},\ \bibinfo {pages} {101003} (\bibinfo
	{year} {2014})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Gulliford}\ \emph {et~al.}(2016)\citenamefont
	{Gulliford}, \citenamefont {Bartnik},\ and\ \citenamefont {Bazarov}}]{gull1}%
\BibitemOpen
\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
		{Gulliford}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Bartnik}},
	\ and\ \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Bazarov}},\ }\href
{\doibase 10.1103/PhysRevAccelBeams.19.093402} {\bibfield  {journal}
	{\bibinfo  {journal} {Phys. Rev. Accel. Beams}\ }\textbf {\bibinfo {volume}
		{19}},\ \bibinfo {pages} {093402} (\bibinfo {year} {2016})}\BibitemShut
{NoStop}%
\bibitem [{\citenamefont {Gulliford}\ \emph {et~al.}(2017)\citenamefont
	{Gulliford}, \citenamefont {Bartnik}, \citenamefont {Bazarov},\ and\
	\citenamefont {Maxson}}]{gull2}%
\BibitemOpen
\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
		{Gulliford}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Bartnik}},
	\bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Bazarov}}, \ and\
	\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Maxson}},\ }\href
{\doibase 10.1103/PhysRevAccelBeams.20.033401} {\bibfield  {journal}
	{\bibinfo  {journal} {Phys. Rev. Accel. Beams}\ }\textbf {\bibinfo {volume}
		{20}},\ \bibinfo {pages} {033401} (\bibinfo {year} {2017})}\BibitemShut
{NoStop}%
\bibitem [{\citenamefont {Kranjčević}\ \emph {et~al.}(2019)\citenamefont
	{Kranjčević}, \citenamefont {Adelmann}, \citenamefont {Arbenz},
	\citenamefont {Citterio},\ and\ \citenamefont {Stingelin}}]{marija}%
\BibitemOpen
\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
		{Kranjčević}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
		{Adelmann}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Arbenz}},
	\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Citterio}}, \ and\
	\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Stingelin}},\ }\href
{\doibase https://doi.org/10.1016/j.nima.2018.12.066} {\bibfield  {journal}
	{\bibinfo  {journal} {Nucl. Instrum. Methods Phys. Res. A}\ }\textbf
	{\bibinfo {volume} {920}},\ \bibinfo {pages} {106 } (\bibinfo {year}
	{2019})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Physics}(2018)}]{gpt}%
\BibitemOpen
\bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
		{Physics}},\ }\href@noop {} {\enquote {\bibinfo {title} {{General Particle
				Tracer (GPT)}},}\ } (\bibinfo {year} {1996-2018}),\ \Eprint
{http://arxiv.org/abs/\url{http://www.pulsar.nl/gpt}}
{\url{http://www.pulsar.nl/gpt}} \BibitemShut {NoStop}%
\bibitem [{\citenamefont {Borland}(2018)}]{elegant}%
\BibitemOpen
\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
		{Borland}},\ }\href@noop {} {\emph {\bibinfo {title} {Elegant: A flexible
			SDDS-compliant code for accelerator simulation}}},\ \bibinfo {type} {Tech.
	Rep.}\ \bibinfo {number} {LS-287}\ (\bibinfo  {institution} {Argonne National
	Laboratory},\ \bibinfo {year} {2000-2018})\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Adelmann}\ \emph {et~al.}(2018)\citenamefont
	{Adelmann}, \citenamefont {Baumgarten}, \citenamefont {Frey}, \citenamefont
	{Gsell}, \citenamefont {Rizzoglio}, \citenamefont {Snuverink}, \citenamefont
	{Metzger-Kraus}, \citenamefont {Ineichen}, \citenamefont {Russell},
	\citenamefont {Wang}, \citenamefont {Sheehy}, \citenamefont {Rogers},\ and\
	\citenamefont {Winklehner}}]{opal}%
\BibitemOpen
\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
		{Adelmann}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
		{Baumgarten}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Frey}},
	\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Gsell}}, \bibinfo
	{author} {\bibfnamefont {V.}~\bibnamefont {Rizzoglio}}, \bibinfo {author}
	{\bibfnamefont {J.}~\bibnamefont {Snuverink}}, \bibinfo {author}
	{\bibfnamefont {C.}~\bibnamefont {Metzger-Kraus}}, \bibinfo {author}
	{\bibfnamefont {Y.}~\bibnamefont {Ineichen}}, \bibinfo {author}
	{\bibfnamefont {S.}~\bibnamefont {Russell}}, \bibinfo {author} {\bibfnamefont
		{C.}~\bibnamefont {Wang}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
		{Sheehy}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Rogers}}, \
	and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Winklehner}},\
}\href@noop {} {\emph {\bibinfo {title} {The {OPAL} (Object Oriented Parallel
			Accelerator Library) Framework}}},\ \bibinfo {type} {Tech. Rep.}\ \bibinfo
{number} {PSI-PR-08-02}\ (\bibinfo  {institution} {Paul Scherrer Institut},\
\bibinfo {year} {2008-2018})\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Bleuler}\ \emph {et~al.}(2003)\citenamefont
	{Bleuler}, \citenamefont {Laumanns}, \citenamefont {Thiele},\ and\
	\citenamefont {Zitzler}}]{pisa}%
\BibitemOpen
\bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
		{Bleuler}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Laumanns}},
	\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Thiele}}, \ and\ \bibinfo
	{author} {\bibfnamefont {E.}~\bibnamefont {Zitzler}},\ }in\ \href@noop {}
{\emph {\bibinfo {booktitle} {{E}volutionary {M}ulti-{C}riterion
			{O}ptimization}}},\ \bibinfo {editor} {edited by\ \bibinfo {editor}
	{\bibfnamefont {C.~M.}\ \bibnamefont {Fonseca}}, \bibinfo {editor}
	{\bibfnamefont {P.~J.}\ \bibnamefont {Fleming}}, \bibinfo {editor}
	{\bibfnamefont {E.}~\bibnamefont {Zitzler}}, \bibinfo {editor} {\bibfnamefont
		{L.}~\bibnamefont {Thiele}}, \ and\ \bibinfo {editor} {\bibfnamefont
		{K.}~\bibnamefont {Deb}}}\ (\bibinfo  {publisher} {Springer},\ \bibinfo
{address} {Berlin, Heidelberg},\ \bibinfo {year} {2003})\ pp.\ \bibinfo
{pages} {494--508}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Deb}(2009)}]{deb:09}%
\BibitemOpen
\bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
		{Deb}},\ }\href@noop {} {\emph {\bibinfo {title} {{M}ulti-{O}bjective
			{O}ptimization {U}sing {E}volutionary {A}lgorithms}}}\ (\bibinfo  {publisher}
{Wiley},\ \bibinfo {year} {2009})\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Kirkpatrick}\ \emph {et~al.}(1983)\citenamefont
	{Kirkpatrick}, \citenamefont {Gelatt},\ and\ \citenamefont
	{Vecchi}}]{kigv:83}%
\BibitemOpen
\bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
		{Kirkpatrick}}, \bibinfo {author} {\bibfnamefont {C.~D.}\ \bibnamefont
		{Gelatt}}, \ and\ \bibinfo {author} {\bibfnamefont {M.~P.}\ \bibnamefont
		{Vecchi}},\ }\href {\doibase 10.1126/science.220.4598.671} {\bibfield
	{journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume}
		{220}},\ \bibinfo {pages} {671} (\bibinfo {year} {1983})}\BibitemShut
{NoStop}%
\bibitem [{\citenamefont {Kennedy}\ and\ \citenamefont
	{Eberhart}(1995)}]{keeb:95}%
\BibitemOpen
\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
		{Kennedy}}\ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
		{Eberhart}},\ }in\ \href {\doibase 10.1109/ICNN.1995.488968} {\emph {\bibinfo
		{booktitle} {Proc. of ICNN}}},\ Vol.~\bibinfo {volume} {4}\ (\bibinfo {year}
{1995})\ pp.\ \bibinfo {pages} {1942--1948}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Dorigo}\ \emph {et~al.}(1996)\citenamefont {Dorigo},
	\citenamefont {Maniezzo},\ and\ \citenamefont {Colorni}}]{domc:96}%
\BibitemOpen
\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
		{Dorigo}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Maniezzo}}, \
	and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Colorni}},\
}\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {IEEE Trans. Syst.
			Man. Cy. B}\ }\textbf {\bibinfo {volume} {26}},\ \bibinfo {pages} {29}
	(\bibinfo {year} {1996})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {De~Castro}\ and\ \citenamefont
	{Timmis}(2002)}]{cati:02}%
\BibitemOpen
\bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
		{De~Castro}}\ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
		{Timmis}},\ }\href@noop {} {\emph {\bibinfo {title} {Artificial immune
			systems: a new computational intelligence approach}}}\ (\bibinfo  {publisher}
{Springer},\ \bibinfo {year} {2002})\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Karaboga}(2005)}]{kara:05}%
\BibitemOpen
\bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
		{Karaboga}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
		{Techn. Rep. TR06, Erciyes Univ. Press, Erciyes}\ } (\bibinfo {year}
	{2005})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Shah-Hosseini}(2009)}]{hoss:09}%
\BibitemOpen
\bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
		{Shah-Hosseini}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
		{Int. J. Bio-Inspir. Com.}\ }\textbf {\bibinfo {volume} {1}},\ \bibinfo
	{pages} {71} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Deb}\ \emph {et~al.}(2002)\citenamefont {Deb},
	\citenamefont {Pratap}, \citenamefont {Agarwal},\ and\ \citenamefont
	{Meyarivan}}]{dpam:02}%
\BibitemOpen
\bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
		{Deb}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Pratap}},
	\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Agarwal}}, \ and\
	\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Meyarivan}},\ }\href
{\doibase 10.1109/4235.996017} {\bibfield  {journal} {\bibinfo  {journal}
		{IEEE Trans. Evol. Comp.}\ }\textbf {\bibinfo {volume} {6}},\ \bibinfo
	{pages} {182} (\bibinfo {year} {2002})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Filipi\v{c}}\ and\ \citenamefont
	{Depolli}(2009)}]{fide:09}%
\BibitemOpen
\bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
		{Filipi\v{c}}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
		{Depolli}},\ }in\ \href {\doibase 10.1007/978-1-84882-409-6\_7} {\emph
	{\bibinfo {booktitle} {Parallel Computing}}},\ \bibinfo {editor} {edited by\
	\bibinfo {editor} {\bibfnamefont {R.}~\bibnamefont {Trobec}}, \bibinfo
	{editor} {\bibfnamefont {M.}~\bibnamefont {Vajter\v{s}ic}}, \ and\ \bibinfo
	{editor} {\bibfnamefont {P.}~\bibnamefont {Zinterhof}}}\ (\bibinfo
{publisher} {Springer},\ \bibinfo {year} {2009})\ pp.\ \bibinfo {pages}
{217--240}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Le\'{o}n}\ \emph {et~al.}(2009)\citenamefont
	{Le\'{o}n}, \citenamefont {Miranda},\ and\ \citenamefont {Segura}}]{lems:09}%
\BibitemOpen
\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
		{Le\'{o}n}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Miranda}}, \
	and\ \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Segura}},\ }\href
{\doibase 10.1142/S0218213009000275} {\bibfield  {journal} {\bibinfo
		{journal} {Int. J. Artif. Intell. Tools}\ }\textbf {\bibinfo {volume} {18}},\
	\bibinfo {pages} {569} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Liefooghe}\ \emph {et~al.}(2007)\citenamefont
	{Liefooghe}, \citenamefont {Basseur}, \citenamefont {Jourdan},\ and\
	\citenamefont {Talbi}}]{lbjt:07}%
\BibitemOpen
\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
		{Liefooghe}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Basseur}},
	\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Jourdan}}, \ and\
	\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Talbi}},\ }in\ \href@noop
{} {\emph {\bibinfo {booktitle} {Evolutionary Multi-Criterion
			Optimization}}}\ (\bibinfo {organization} {Springer},\ \bibinfo {year}
{2007})\ pp.\ \bibinfo {pages} {386--400}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Durillo}\ \emph {et~al.}(2006)\citenamefont
	{Durillo}, \citenamefont {Nebro}, \citenamefont {Luna}, \citenamefont
	{Dorronsoro},\ and\ \citenamefont {Alba}}]{dnld:06}%
\BibitemOpen
\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
		{Durillo}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Nebro}},
	\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Luna}}, \bibinfo {author}
	{\bibfnamefont {B.}~\bibnamefont {Dorronsoro}}, \ and\ \bibinfo {author}
	{\bibfnamefont {E.}~\bibnamefont {Alba}},\ }\href@noop {} {\emph {\bibinfo
		{title} {jMetal: a java framework for developing multi-objective optimization
			metaheuristics}}},\ \bibinfo {type} {Tech. Rep.}\ \bibinfo {number}
{ITI-2006-10}\ (\bibinfo  {institution} {University of M{\'a}laga, ETSI
	Inform{\'a}tica, Campus de Teatinos},\ \bibinfo {year} {2006})\BibitemShut
{NoStop}%
\bibitem [{\citenamefont {Arbenz}\ and\ \citenamefont
	{Chinellato}(2008)}]{ARBENZ2008381}%
\BibitemOpen
\bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
		{Arbenz}}\ and\ \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
		{Chinellato}},\ }\href {\doibase 10.1016/j.apnum.2007.01.019} {\bibfield
	{journal} {\bibinfo  {journal} {Appl. Numer. Math.}\ }\textbf {\bibinfo
		{volume} {58}},\ \bibinfo {pages} {381} (\bibinfo {year} {2008})}\BibitemShut
{NoStop}%
\bibitem [{boo(2015)}]{boost}%
\BibitemOpen
\href@noop {} {\enquote {\bibinfo {title} {{The Boost Spirit Home Page}},}\ }
(\bibinfo {year} {2015}),\ \bibinfo {note}
{\url{http://boost-spirit.com/}}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {{ E. Friedman and I. Maman }}(2003)}]{boost2}%
\BibitemOpen
\bibfield  {author} {\bibinfo {author} {\bibnamefont {{ E. Friedman and I.
				Maman }}},\ }\href@noop {} {\enquote {\bibinfo {title} {{Chapter 45.
				Boost.Variant}},}\ } (\bibinfo {year} {2003}),\ \bibinfo {note}
